---
title: "Flood Zone Screening"
format:
  html:
    embed-resources: true
    toc: false
    page-layout: full
params:
  lat: 49.883400567909774
  lon: -96.93126342501104
  address: "Cobalt Road"
  job_id: "26029115"
  zoom: 11
  proximity_threshold_m: 500
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
suppressPackageStartupMessages({
  library(sf)
  library(leaflet)
  library(dplyr)
  library(gt)
  library(htmltools)
})
source("R/analyze_subject.R")

result <- analyze_subject(
  lat = params$lat,
  lon = params$lon,
  data_dir = "data",
  proximity_threshold_m = params$proximity_threshold_m
)
```

::: {style="font-family:system-ui; margin-bottom:1em;"}
**Job:** `r params$job_id` &nbsp;·&nbsp; **Address:** `r params$address`
**Subject coordinates:** `r sprintf("%.5f, %.5f", params$lat, params$lon)` &nbsp;·&nbsp; **Rendered:** `r format(Sys.Date())`
:::

## Screening Conclusion

```{r conclusion-table}
result$table |>
  mutate(
    `Subject inside?` = ifelse(is.na(inside), "—", ifelse(inside, "Yes", "No")),
    `Nearest extent (m)` = ifelse(is.na(nearest_m), "—",
                                  ifelse(nearest_m == 0, "0 (within)",
                                         format(round(nearest_m), big.mark = ",")))
  ) |>
  select(Layer = layer, `Subject inside?`, `Nearest extent (m)`, Source = source, Refreshed = refreshed, Note = note) |>
  gt() |>
  tab_style(
    style = list(cell_fill(color = "#ffe5e5"), cell_text(weight = "bold")),
    locations = cells_body(
      columns = `Subject inside?`,
      rows = `Subject inside?` == "Yes"
    )
  ) |>
  tab_options(table.font.size = px(13), data_row.padding = px(4))
```

## Copy-Ready Appraisal Paragraph

::: {style="border:1px solid #bbb; padding:12px 16px; background:#f8f8f8; border-radius:6px; font-family:Georgia,serif; line-height:1.5;"}
`r result$paragraph`
:::

## Interactive Map

```{r leaflet-map}
#| out-width: "100%"
#| out-height: "720px"
layer_files <- list(
  `1997 Flood`                              = list(path = "data/red_river_flood_1997.geojson",        color = "#d62728"),
  `2009 Flood`                              = list(path = "data/red_river_flood_2009.geojson",        color = "#ff7f0e"),
  `2011 Flood`                              = list(path = "data/red_river_flood_2011.geojson",        color = "#1f77b4"),
  `1-in-200 Extent`                         = list(path = "data/mb_1in200_flood_extent.geojson",      color = "#9467bd"),
  `Red River Valley DFA`                    = list(path = "data/dfa_all.geojson",                     color = "#2ca02c"),
  `Lower Red River DFA`                     = list(path = "data/dfa_lower_red_river.geojson",         color = "#17becf"),
  `RRV Special Management Area`             = list(path = "data/rrv_special_management_area.geojson", color = "#8a6d3b"),
  `Winnipeg Waterway — Rivers (107 m)`      = list(path = "data/wpg_waterway_river_corridor.geojson", color = "#1e88e5"),
  `Winnipeg Waterway — Creeks (76 m)`       = list(path = "data/wpg_waterway_creek_corridor.geojson", color = "#5ebadf")
)

popup_html <- sprintf("<b>%s</b><br/>%.5f, %.5f", params$address, params$lat, params$lon)

red_icon <- awesomeIcons(icon = "home", library = "fa",
                         markerColor = "red", iconColor = "white")

m <- leaflet() |>
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite") |>
  addProviderTiles(providers$CartoDB.Positron, group = "Roads") |>
  setView(lng = params$lon, lat = params$lat, zoom = params$zoom) |>
  addScaleBar(position = "bottomleft")

for (nm in names(layer_files)) {
  f <- layer_files[[nm]]
  if (!file.exists(f$path)) next
  poly <- read_sf(f$path, quiet = TRUE) |> st_transform(4326)
  m <- addPolygons(m, data = poly,
                   color = f$color, weight = 1.5, opacity = 0.9,
                   fillColor = f$color, fillOpacity = 0.30,
                   group = nm, label = nm)
}

m <- m |>
  addAwesomeMarkers(lng = params$lon, lat = params$lat,
                    icon = red_icon,
                    popup = popup_html,
                    label = params$address,
                    labelOptions = labelOptions(permanent = TRUE, direction = "top",
                                                offset = c(0, -40),
                                                style = list("font-weight" = "bold"))) |>
  addLayersControl(
    baseGroups = c("Roads", "Satellite"),
    overlayGroups = names(layer_files),
    options = layersControlOptions(collapsed = FALSE)
  ) |>
  addLegend(
    position = "bottomright",
    colors = unname(sapply(layer_files, `[[`, "color")),
    labels = names(layer_files),
    opacity = 0.7,
    title = "Flood layers"
  ) |>
  hideGroup("RRV Special Management Area")

m
```

## Static Exhibit (PNG)

```{r export-png}
#| eval: !expr 'requireNamespace("webshot2", quietly = TRUE)'
slug <- function(x) gsub("_+", "_", gsub("[^A-Za-z0-9]+", "_", trimws(x)))
png_path <- file.path("outputs", params$job_id)
dir.create(png_path, recursive = TRUE, showWarnings = FALSE)
png_name <- sprintf("%s_%s.png", slug(params$job_id), slug(params$address))
png_file <- file.path(png_path, png_name)
tryCatch({
  m_png <- m
  m_png$width  <- 900
  m_png$height <- 500
  tmp_html <- tempfile(fileext = ".html")
  htmlwidgets::saveWidget(m_png, tmp_html, selfcontained = TRUE)
  webshot2::webshot(tmp_html, file = png_file,
                    vwidth = 900, vheight = 500, zoom = 1.5,
                    cliprect = "viewport", delay = 1)
  cat("PNG exhibit saved to:", png_file, "\n")
}, error = function(e) {
  cat("PNG export failed:", conditionMessage(e), "\n")
})
```


## Sources & Methodology

```{r sources}
layers_meta <- yaml::read_yaml("data/layers.yml")$layers
tibble::tibble(
  Layer    = vapply(layers_meta, function(x) x$label, character(1)),
  Source   = vapply(layers_meta, function(x) x$source, character(1)),
  CRS      = vapply(layers_meta, function(x) x$native_crs, character(1)),
  Features = vapply(layers_meta, function(x) x$feature_count, integer(1)),
  Refreshed = vapply(layers_meta, function(x) substr(x$refreshed_iso, 1, 10), character(1)),
  URL      = vapply(layers_meta, function(x) x$url, character(1))
) |>
  gt() |>
  fmt_url(columns = URL, label = "link") |>
  tab_options(table.font.size = px(11), data_row.padding = px(2))
```

::: {style="font-size:11px; color:#666; margin-top:1em;"}
Distances computed in EPSG:3347 (Statistics Canada Lambert). Subject inside-test uses `sf::st_within`; nearest-extent uses `sf::st_distance`.
The Manitoba 1-in-200 year flood extent layer is served with geometry simplification (~50 m tolerance) to keep the cached file compact; boundary determinations within ~50 m of the extent edge should be verified against the authoritative source.
:::
